beastscriptr: BEAUti for R

### 2017-10-09 prevstyle/main.tex
Change to new style

\abstract{\textbf{Motivation:} BEAST2 is a popular Bayesian phylogenetics tool.
The program BEAUti allows for a user-friendly way to create the
input files that BEAST2 needs. This is convenient to get started, yet
does not facilitate the scripted use of BEAST2. 
beastscriptr is an R package that can create BEAST2 input files from an R
function call.\\
\textbf{Results:} beastscriptr has only parts of the functionality of BEAUti, yet
can be extended easily. beastcriptr, on the other hand, does allow for specifying
to use phylogenies of fixed crown age.\\
\textbf{Availability:} The package is free and is available from the official R package archive at 
http://cran.r-project.org/src/contrib/PACKAGES.html\#beastscriptr. 
beastscriptr is licensed under the GNU General Public License.
\textbf{Contact:} \href{name@bio.com}{name@bio.com}\\
\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics}
online.}

@@

BEAST2 \cite{bouckaert2014beast} is a popular Bayesian phylogenetics tool.
The program BEAUti \cite{drummond2012bayesian} allows for a user-friendly 
way to create the
input files that BEAST2 needs. This is convenient to get started, yet
does not facilitate the scripted use of BEAST2. 
beastscriptr is an R package that can create BEAST2 input files from an R
function call.

@@

The goal of the R package beastscriptr was to mimic the functionality of BEAUti.
Where BEAUti creates a BEAST2 XML input file by a graphical user interface,
beastscriptr would do the same from one R function call.

@@

By creating BEAST2 input files in BEAUti, the files beastscriptr should
create were determined. BEAUti already has many options, already
before taking all possible plug-ins into account. beastscriptr 
gradually grew in mimicking the basic functionality of BEAUti.

@@

This work has been supported by the VICI of Rampal S. Etienne.

>>>>

\abstract{\textbf{Motivation:} BEAST2 is a popular Bayesian phylogenetics tool.
The program BEAUti allows for a user-friendly way to create the
input files that BEAST2 needs. This is convenient to get started, yet
does not facilitate the scripted use of BEAST2. 
beastscriptr is an R package that can create BEAST2 input files from an R
function call.\\
\textbf{Results:} beastscriptr has only parts of the functionality of BEAUti, yet
can be extended easily. beastcriptr, on the other hand, does allow for specifying
to use phylogenies of fixed crown age.\\
\textbf{Availability:} The package is free and is available from the official R package archive at 
http://cran.r-project.org/src/contrib/PACKAGES.html\#beastscriptr. 
beastscriptr is licensed under the GNU General Public License.
\textbf{Contact:} \href{r.j.c.bilderbeek@rug.nl}{r.j.c.bilderbeek@rug.nl}\\
\textbf{Supplementary information:} Supplementary data are available at \textit{Bioinformatics}
online.}

@@

BEAST2 \cite{bouckaert2014beast} is a popular Bayesian phylogenetics tool.
BEAST2 is bundled with the program called BEAUti \cite{drummond2012bayesian},
which  allows for a user-friendly way to create the
input files that BEAST2 needs. This is convenient to get started, yet
does not allow for the scripted use of BEAST2. beastscriptr is an R package 
that can create BEAST2 input files from an R function call.

@@

The goal of the R package beastscriptr is to create the 
same BEAST2 input files that BEAUti creates, but from one R function call 
instead.

@@

By creating BEAST2 input files in BEAUti, 
the desired output of beastscriptr was determined. 
The functionality of BEAUti is added gradually (and is still growing).

@@

???This work has been supported by the VICI of Rampal S. Etienne.
